%
% Daftar Pustaka 
% 

% 
% Tambahkan pustaka yang digunakan setelah perintah berikut. 
%
\phantomsection 
\begin{thebibliography}{15}

\bibitem{latex.intro}
{Jeff Clark. (n.d). \f{Introduction to LaTeX}.
26 Januari 2010. \url{http://frodo.elon.edu/tutorial/tutorial/node3.html}.}
\bibitem{reqm.collaborative}
{Lin, J.J.Y., Lin, Y. S. \f{Collaborative Requirement Management System Developed for CMMI-Coherent Software Engineering. In: 11th International Conference on Computer Supported Cooperative Work in Design pp.657-662}. IEEE Press (2007).}
\bibitem{reqm.cad}
{Karwowski, K., Wysota, W., Wytre¸bowicz, J. \f{Computer Aided Requirements Management. In: Proceedings of the 1st international Conference on Computational Collective intelligence. Semantic Web, Social Networks and Multiagent Systems} (WrocBaw, Poland). Nguyen, N. T., Kowalczyk, R., and Chen, S., (Eds). LNAI 5796, pp. 389-400. Springer-Verlag, Berlin, Heidelberg (2009).}
\bibitem{reqm.interface}
{Hood, C., Wiedemann, S., Fichtinger, S., Pautz, U. \f{Requirements Management: The Interface Between Requirements Development and All Other System Engineering Process}. Springer, Heidelberg-Berlin (2008).}
\bibitem{reqm.requirements}
{Hoffmann, M., Kuhn, N., Weber, M., Bittner, M. \f{ Requirements for Requirements Management Tools. In: 12th IEEE International Requirements Engineering Conference 2004, pp. 301- 308}. IEEE Press (2004).}
\bibitem{reqm.web}
{\f{CMMI - Requirements Management (REQM) Process Area} \url{http://www.software-quality-assurance.org/cmmi-requirements-management.html}. Diakses 10 Desember 2010}
\bibitem{reqm.cmmidev}
{\href{http://www.sei.cmu.edu/library/abstracts/reports/10tr033.cfm}{\f{CMMI for Development, Version 1.3}} (pdf). \f{CMMI-DEV} (Versi 1.3, November 2010). Carnegie Mellon University Software Engineering Institute (2010). Diakses 10 Desember 2010.}
\bibitem{reqm.cmmiforswcontinous}
{\href{http://www.sei.cmu.edu/library/abstracts/reports/02tr028.cfm}{\f{CMMI for Software Engineering, Version 1.1. Continous Representation}} (pdf). \f{CMMI-DEV} (Versi 1.1, Agustus 2002). Carnegie Mellon University Software Engineering Institute (2002). Diakses 10 Desember 2010.}
\bibitem{reqm.cmmiforswstaged}
{\href{http://www.sei.cmu.edu/library/abstracts/reports/02tr029.cfm}{\f{CMMI for Software Engineering, Version 1.1. Staged Representation}} (pdf). \f{CMMI-DEV} (Versi 1.1, Agustus 2002). Carnegie Mellon University Software Engineering Institute (2002). Diakses 10 Desember 2010.}
\bibitem{reqm.distilled}
{Ahern, D. M., Clouse, A., Turner, R. \f{CMMI® Distilled: A Practical Introduction to Integrated Process Improvement, Third Edition}. Addison Wesley (2008).}
\bibitem{reqm.managing}
{Leffingwell, D., Widrig, D. \f{Managing Software Requirements: A Unified Approach}. Addison Wesley (1999).}
\bibitem{reqm.practical}
{Kasse, T., Practical Insights into CMMI®, Second Edition. Artech House, Inc (2008).}
\end{thebibliography}

